---
title: "Assignment 4"
author: "M. Hill"
date: "10/21/2024"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Exercise 1
a) This regular expression matches: 
Strings that contain 'ab' in that order only.
```{r}
strings <- c('ab','acb','cab','bac')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, 'ab') )
```

b) This regular expression matches:
Strings that contain 'a' or 'b'.
```{r}
strings <- c('bat','did','goa','less')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '[ab]') )
```

c) This regular expression matches:
Strings that contain 'a' or 'b' at the beginning.
```{r}
strings <- c('boy','goal','apple','labs')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '^[ab]') )
```

d) This regular expression matches:
Strings that contains one or more repetition of a digit, then a whitespace, then
'a' or 'A'.
```{r}
strings <- c('525 A', 'aa a', '2 a','2A')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '\\d+\\s[aA]') )
```

e) This regular expression matches:
Strings that contain one or more repetitions of a digit, then zero or more 
repetitions of a white space, then a or A.
```{r}
strings <- c('HOUSE:3A','HOUSE:3 ',' NO 3 HOUSE:3A','4davros A')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '\\d+\\s*[aA]') )
```

f) This regular expression matches:
Strings that contain zero or more repetitions of any character.
```{r}
strings <- c('','superpowerflowerpollen2','45','&&')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '.*') )
```

g) This regular expression matches:
Strings that start with two repetitions of any alphanumeric character and 'bar' exactly
```{r}
strings <- c('22bar','Aebar','AAbaer','barYES!')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '^\\w{2}bar') )
```

h) This regular expression matches:
Strings that contain the group contain 'foo', then a period, followed by 'bar',
or the string starts with two repetitions of any alphanumeric character and 'bar' exactly.
```{r}
strings <- c('AAfoo.bar','anaownwko foobar','76barfoo.9','A2foobar')
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '(foo\\.bar)|(^\\w{2}bar)') )
```

## Exercise 2
```{r}
file.names <- c( 'S123.P2.C10_20120621_213422.jpg',
                 'S10.P1.C1_20120622_050148.jpg',
                 'S187.P2.C2_20120702_023501.jpg')
temp <- data.frame(site = str_extract(file.names, 'S\\d+'),
    plot = str_extract(file.names, 'P\\d+')
  )

temp
```








