---
title: "Assignment 3"
author: "M Hill"
date: "10/11/2024"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Exercise 1
(a)
```{r}
duniform <- function(x,a,b)
{
  
  n <- NULL
  
  if (x >= a & x <= b)
  {
    n <- (1/b-a)
  }
  else
  {
    n <- 0
  }
  
  return(n)

}

duniform(2,6,8)
duniform(7,6,8)
duniform(9,6,8)
```

(b)
```{r}
duniform <- function(x,a,b)
{
  n <- c()
  for (i in 1:length(x))
  {
    if (x[i] >= a & x[i] <= b)
    {
      n[i] <- (1/(b-a))
    }
    else
    {
      n[i] <- 0
    }
  }

  return(n)

}

data.frame( x=seq(-1, 12, by=.001) ) %>%
  mutate( y = duniform(x, 4, 8) ) %>%
  ggplot( aes(x=x, y=y) ) +
  geom_step()
```
(c)
```{r}
microbenchmark::microbenchmark( duniform( seq(-4,12,by=.0001), 4, 8), times=100)
```
(d)
```{r}
duniform <- function(x,a,b)
{
  n <- ifelse(x >= a & x <= b,1/(b-a),0)
  return(n)
}

data.frame( x=seq(-1, 12, by=.001) ) %>%
  mutate( y = duniform(x, 4, 8) ) %>%
  ggplot( aes(x=x, y=y) ) +
  geom_step()

microbenchmark::microbenchmark( duniform( seq(-4,12,by=.0001), 4, 8), times=100)
```
(e)

The ifelse was easier to write than the for loop, once i got some of the syntax down. And it ran much faster than the for loop I wrote.

## Exercise 2
```{r}
duniform <- function(x,a=0,b=1)
{
  n <- ifelse(x >= a & x <= b,1/(b-a),0)
  return(n)
}

data.frame( x=seq(-1, 12, by=.001) ) %>%
  mutate( y = duniform(x) ) %>%
  ggplot( aes(x=x, y=y) ) +
  geom_step()
```

Setting a=0 and b=1, creates default that the function will use when it is called without those arguments.

## Exercise 3
(a)
```{r}
standardize <- function(x)
{
  n <- c()
  mtn <- mean(x)
  std <- sd(x)
  for (i in 1:length(x))
  {
    
    n[i] <- (x[i] - mtn)/std
    
  }
  
  return(n)
}



```
(b)
```{r}
data( 'iris' )
# Graph the pre-transformed data.
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point() +
  labs(title='Pre-Transformation')

# Standardize all of the numeric columns
# across() selects columns and applies a function to them
# there column select requires a dplyr column select command such
# as starts_with(), contains(), or where().  The where() command
# allows us to use some logical function on the column to decide
# if the function should be applied or not.
iris.z <- iris %>% mutate( across(where(is.numeric), standardize) )

# Graph the post-transformed data.
ggplot(iris.z, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point() +
  labs(title='Post-Transformation')

```

I created a vector within the function that would hold and then return the standardized numeric variables.

## Exercise 4
```{r}
fizzBuzz <- function(n)
{
  fizzList <- c()
  for (i in 1:n)
  {
    if (i %% 15 == 0)
    {
      fizzList[i] = "Fizz-Buzz"
    }
    else if (i %% 5 == 0)
    {
      fizzList[i] = "Buzz"
    }
    else if (i %% 3 == 0)
    {
      fizzList[i] = "Fizz"
    }
    else
    {
      fizzList[i] = i
    }
  }
  return(fizzList)

}
fizzBuzz(30)

```

The fizzBuzz function loops from one to n. Then, based on the if and else statements places the results, either "Fizz", "Buzz", "Fizz-Buzz", and the number itself into a vector that is returned.







