---
title: "Assignment 5"
author: "M. Hill"
date: "10/28/2024"
output: pdf_document
---

```{r setup, include=FALSE}
library(lubridate)
library(tidyverse)
library(mosaicData)
```

## Exercise 1
a)
```{r}
mdy("September 13, 2010")
```
b)
```{r}
mdy("Sept 13, 2010")
```
c)
```{r}
mdy("Sep 13, 2010")
```
d)
```{r}
mdy("S 13, 2010")
```
Abbreviations of months need to be the first three letters of the month.

e)
```{r}
mdy("07-Dec-1941")
```
f)
```{r}
mdy("1-5-1998")
```
Using single digits for both the month and day makes it hard to know which is the
month or day.

g)
```{r}
dmy("21-5-1998")
```
It is clear to see which is the day, and which is the month.
h)
```{r}
ymd_hm("2020-May-5 10:30 am")
```
i)
```{r}
ymd_hm("2020-May-5 10:30 am PDT (ex Seattle)")
```
j)
```{r}
ymd_hm("2020-May-5 10:30 am AST (ex Puerto Rico)")
```

## Exercise 3
```{r}
dates <- c("May-8-2025 3:00 PM","May-8-2025 3:00 PM")
zones <- c("US/Arizona","Pacific/Auckland")
data.frame(date = dates, zone = zones) %>%
  rowwise() %>%
  mutate(date = mdy_hm(date,tz = zone))
```
After finding what the tz identifier was for Auckland, New zealand. I applied
each timezone rowwise as only a single timezone can be sent to the dates vector.

## Exercise 5
a)
```{r}
births1 <- Births78 %>%
  select(date,births)

```
b)
```{r}
births1 %>%
  ggplot(aes(x = date, y = births)) +
  geom_point()
```
There are almost two graphs, it seems consistently there are certain days
which have much more births than other days. I think it might be people having 
kids on weekends.

C)
```{r}
births2 <- births1 %>%
  mutate(dow = wday(date, label=TRUE, abbr=FALSE))
```
d)
```{r}
births2 %>%
  ggplot(aes(x = date, y = births)) +
  geom_point(aes(color = dow))
```













